---
author: "Bogdan Jastrzębski"
title: "Tutorial for Linear Regression Example Package"
date: "March 20, 2025"
output: html_document
---


# Linear Regression Tutorial

The following is a tutorial for a [linear regression](https://www.youtube.com/watch?v=dQw4w9WgXcQ&ab_channel=RickAstley) package
created for the project 2 of **Advanced R Programming** course,
2025, summer semester. The code can be found in [the github repository][1].

## Package Installation

Install the package from [the github repository][1]:
```{r}
devtools::install_github(repo = "bogdankjastrzebski/ARP2025LProject2", force=TRUE)
```
and load the library:
```{r}
library(ARP2025LProject2)
```

## Linear Regression Usage

The library exports the following functions:

* `S3method(plot,linreg)`
* `export(evaluate)`
* `export(generate_data)`
* `export(linear_regression)`

Generate fake data:
```{r}
linreg_data = generate_data(128, 16)

X = linreg_data$X
Y = linreg_data$Y
B = linreg_data$B
```
the data looks roughly like this:
```{r}
knitr::kable(round(data.frame(head(X)), 2), caption="First rows of our generated data.")
```

Fit the model to the data with L2 regularization:
```{r}
linreg = linear_regression(X, Y, reg=0.1)
```

Plot residuals:
```{r}
plot(linreg)
```

# Discussion

The residual plot should show a sample from the normal distribution.
Otherwise you should probably use a different model.

If we make 100 row training set and 28 validation, the `evaluate` function:

| r.squared | adj.r.squared | mse |
|---|---|---|
| 0.9415951 | 0.8566425 | 1.768494 |


# Project Checklist:
- [x] headings of different sizes (minimum two),
- [x] at least three chunks,
- [x] a list,
- [x] a hyperlink,
- [x] a plot,
- [x] and a table.


# References
1. ["A tutorial on linear regression models. 202, Journal of Applied Statistics and Data Mining, 2005"][2]

[1]: https://github.com/bogdankjastrzebski/ARP2025LProject2 "the github repository"
[2]: https://www.youtube.com/watch?v=dQw4w9WgXcQ&ab_channel=RickAstley "linear regression"
